Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2015-09-09 paper.tex
Fix citation
Some spacing and wrapping

\begin{figure}
    \centering
    \begin{subfigure}[b]{\textwidth}
        \centering \includegraphics[clip, trim=0 0.1in 0 0.2in,
        width=0.75\textwidth]{figures/meancontquiv_exp} \caption{Mean velocity
            field at $x/D=1$ from experiments \cite{Bachant2015-RVAT-Re-dep-data}.}
        \label{fig:meancontquiv-exp}
    \end{subfigure}

    \begin{subfigure}[b]{\textwidth}
        \centering \includegraphics[clip, trim=0 0.2in 0 0.15in,
        width=0.8\textwidth]{figures/meancontquiv_kOmegaSST} \caption{Mean
            velocity at $x/D=1$ computed by the 3-D SST model.}
        \label{fig:meancontquiv-SST}
    \end{subfigure}

    \begin{subfigure}[b]{\textwidth}
        \centering \includegraphics[clip, trim=0 0.2in 0 0.15in,
        width=0.8\textwidth]{figures/meancontquiv_SpalartAllmaras} \caption{Mean
            velocity at $x/D=1$ computed by the 3-D SA model.}
        \label{fig:meancontquiv-SA}
    \end{subfigure}

@@

    \caption{Weighted sum normalized momentum recovery terms for each CFD case
        and experiments\cite{Bachant2015-JoT} at $x/D=1$.}

>>>>

\begin{figure}
    \centering
    \begin{subfigure}[b]{\textwidth}
        \centering

        \includegraphics[clip, trim=0 0.1in 0 0.2in,
        width=0.75\textwidth]{figures/meancontquiv_exp}

        \caption{Mean velocity field at $x/D=1$ from experiments
            \cite{Bachant2015-RVAT-Re-dep-data}.}

        \label{fig:meancontquiv-exp}
    \end{subfigure}

        \includegraphics[clip, trim=0 0.2in 0 0.15in,
        width=0.8\textwidth]{figures/meancontquiv_kOmegaSST}

        \caption{Mean velocity at $x/D=1$ computed by the 3-D SST model.}

        \label{fig:meancontquiv-SST}
    \end{subfigure}

        \includegraphics[clip, trim=0 0.2in 0 0.15in,
        width=0.8\textwidth]{figures/meancontquiv_SpalartAllmaras}

        \caption{Mean velocity at $x/D=1$ computed by the 3-D SA model.}

        \label{fig:meancontquiv-SA}
    \end{subfigure}

@@

    \caption{Weighted sum normalized momentum recovery terms for each CFD case
        and experiments\cite{Bachant2015-RVAT-Re-dep-data} at $x/D=1$.}
